Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-07-27 paper/amia.tex
Auto Update from local Sharelatex

\author{
  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett$^{1,2}$, MD, MS, Debashis Ghosh, PhD$^{1,3}$
  }

@@

KFP provides multiple methods by which a health data scientist can access on-demand faux-data. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method. Data can either be viewed directly in browser or downloaded in csv format for use in a ML process. Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query. In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.

>>>>

\author{
  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett, MD, MS$^{1,2}$,\\ Debashis Ghosh, PhD$^{1,3}$
  }

@@

KFP provides multiple methods by which a health data scientist can access on-demand faux-data. As shown in Figure~\ref{fig:ui}, a single page web application (SPA) allows for users to directly enter SQL queries, submit them to the connected database, and receive faux-data according to the selected generation method. The SPA additionally allows for the upload of csv files (not shown) to allow for ease of evaluation and testing of the provided data synthesis methods. Faux-data can either be viewed directly in browser or downloaded in csv format for use in a ML process. Alternatively, a Hypertext Transfer Protocol (HTTP) Representational State Transfer (REST) service \cite{w3c_working_group_webservices}, utilized by the SPA, allows for cross language compatible requesting and receiving of faux-data, again via SQL query. In order to facilitate querying and understanding of the data model, the database metadata is presented to the user in a collapsible section. Lastly, for Python based software or languages with an interface to Python, the kungfauxpandas.py file and associated classes can be imported and called natively.
